### 2023-01-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@c996e47ff1b1567c3517efc1a6d065ac6522a5ab 🚀

\begin{figure}
\hypertarget{fig:geometric}{%
\centering
\includegraphics{./figures/fig1.png}
\caption{\textbf{(A)} The probability that an observed interaction is a
true negative (y-axis) given how many times it has been sampled as a
non-interaction (x-axis). Each color reflects a different value of
\(p_{fn}\), the false-negative-rate (FNR)---this is effectively the cdf
of the geometric distribution. \textbf{(B)} The expected number of total
observations needed (colors) to observe 10 co-occurrences between a
species with relative abundance \(P(A)\) (x-axis) and a second species
with relative abundance \(P(Y)\). \textbf{(C)}: false-negative-rate
(y-axis) as a function of total sampling effort (x-axis) and network
size, computed using the method described above. For 500 independent
draws from the niche model (Williams \& Martinez (2000)) at varying
levels of species richness (colors) with connectance drawn according to
the flexible-links model (MacDonald \emph{et al.} (2020)) as described
in the main text. For each draw from the niche model, 200 sets of 1500
observations are simulated, for which the mean false-negative-rate at
each observation-step is computed. Means denoted with points, with 1 in
the first shade and 2 in the second. \textbf{(D)}: Same as \textbf{(C)},
except using empirical food webs from Mangal database, where richness.
The outlier on \textbf{(D)} is a 714 species
food-web.}\label{fig:geometric}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:resampling_concept}{%
\centering
\includegraphics{./figures/uncertainty_sampler.png}
\caption{(A) The process for estimating the false-negative-rate (FNR)
for an interaction dataset consisting of \(N\) total observed
interactions. (B) The method for resampling interaction probability
based on estimates of false-negative and false-positive rates. (C) The
method for interaction probability resampling applied to three mammals
and three parasites from the Hadfield \emph{et al.} (2014)
dataset.}\label{fig:resampling_concept}
}
\end{figure}

@@

We can then further truncate to remain on the interval \((0,1)\) (as the
output is a probability, although in practice often the probability mass
outside \((0,1)\) is exteremly low. As an example case study, we use a
boosted-regression-tree to predict interactions in a host-parasite
network (Hadfield \emph{et al.} 2014) (with features derived in the same
manner as Strydom \emph{et al.} (2021) derives features on this data) to
produce a set of interaction predictions. We then applied this method to
a set of a few resampled interaction probabilities between mammals and
parasite species shown in figure fig.~\ref{fig:resampling_concept}(C).

Why is this useful? For one, this analytic method avoids the extra
computation required by simulating samples from this distribution
directly. Further, it enables continuous exanination of the number of
particles \(n_p\) as a uncertainty width. The natural analogue for the
number of particles sampled is the number of observations of
co-occurrence for a given pair of species---the fewer the particles, the
higher the variance of the resulting approximation. The normal
approximation is undefined for 0 particles (i.e.~0 observations
co-occurrence), although as \(n_p\) approaches \(0\) the approxated
normal (once truncated) approaches a uniform distribution on the
interval \((0,1)\), the maximum entropy distribution where we have no
information about the possibility of an interaction.

>>>>

\begin{figure}
\hypertarget{fig:geometric}{%
\centering
\includegraphics{./figures/fig1.png}
\caption{\textbf{(A)} The probability that an observed interaction is a
true negative (y-axis) given how many times it has been sampled as a
non-interaction (x-axis). Each color reflects a different value of
\(p_{fn}\), the false-negative-rate (FNR)---this is effectively the
cumulative distribution function (cdf) of the geometric distribution.
\textbf{(B)} The expected number of total observations needed (colors)
to observe 10 co-occurrences between a species with relative abundance
\(P(A)\) (x-axis) and a second species with relative abundance \(P(Y)\).
\textbf{(C)}: false-negative-rate (y-axis) as a function of total
sampling effort (x-axis) and network size, computed using the method
described above. For 500 independent draws from the niche model
(Williams \& Martinez (2000)) at varying levels of species richness
(colors) with connectance drawn according to the flexible-links model
(MacDonald \emph{et al.} (2020)) as described in the main text. For each
draw from the niche model, 200 sets of 1500 observations are simulated,
for which the mean false-negative-rate at each observation-step is
computed. Means denoted with points, with 1 in the first shade and 2 in
the second. \textbf{(D)}: Same as \textbf{(C)}, except using empirical
food webs from Mangal database, where richness. The outlier on
\textbf{(D)} is a 714 species food-web.}\label{fig:geometric}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:resampling_concept}{%
\centering
\includegraphics{./figures/uncertainty_sampler.png}
\caption{(A) The process for estimating the false-negative-rate (FNR)
for an interaction dataset consisting of \(N\) total observed
interactions. (B) The method for resampling interaction probability
based on estimates of false-negative and false-positive rates. (C) The
method for interaction probability resampling applied to three mammals
and three parasites from the Hadfield \emph{et al.} (2014) dataset. The
original probability \(p_{ij}\) is indicated with a vertical dashed
line. The histogram is simulated from the resampling process, and the
line indicates the gaussian approximation to this
distribution.}\label{fig:resampling_concept}
}
\end{figure}

@@

We can then further truncate to remain on the interval \((0,1)\) (as the
output is a probability, although in practice often the probability mass
outside \((0,1)\) is extremely low. As an example case study, we use a
boosted-regression-tree to predict interactions in a host-parasite
network (Hadfield \emph{et al.} 2014) (with features derived in the same
manner as Strydom \emph{et al.} (2021) derives features on this data) to
produce a set of interaction predictions. We then applied this method to
a set of a few resampled interaction probabilities between mammals and
parasite species shown in figure fig.~\ref{fig:resampling_concept}(C).

Why is this useful? For one, this analytic method avoids the extra
computation required by simulating samples from this distribution
directly. Further, it enables continuous extension of the number of
particles \(n_p\) as a uncertainty width. The natural analogue for the
number of particles sampled is the number of observations of
co-occurrence for a given pair of species---the fewer the particles, the
higher the variance of the resulting approximation. The normal
approximation is undefined for 0 particles (i.e.~0 observations
co-occurrence), although as \(n_p\) approaches 0 the approximated normal
(once truncated) approaches a uniform distribution on the interval
\((0,1)\), the maximum entropy distribution where we have no information
about the possibility of an interaction.
